% This is a variation of the NeurIPS'24 format
\documentclass{article}
\usepackage[final]{adrl}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}     
\usepackage{algorithm}
\usepackage{algpseudocode}

% Add your own as neccessary

\title{RL Project Report Template}
\author{Theo Retisch \\ \url{github.com/theo/adrl_project}}

\begin{document}

\maketitle
\begin{abstract}
    An abstract is a short summary of your project. It should really only be a single paragraph, not much more than 10 lines.
\end{abstract}
\section{Introduction}
This is your motivational section: describe the setting, your research questions and why they're important! This should be pretty similar to a paper's introduction section, but a bit shorter.

\section{Related Work}
Here you cite related papers, either by referring to \cite{parkerholder-jair22} or as a reference at the end of the sentence~\citep{parkerholder-jair22}. 
Add your references to the "references.bib" file. 
Pay attention: if you get the citation from arxiv, it will only give you that version -- but you should cite the conference or journal version if it exists! 
Therefore, you should look for the paper on dblp.org and use that citation. 
You can delete things like the bibsource and timestamp, but keep the important information like authors, title, journal, year or DOI.

You do not need to cite papers just to have a certain number of citations, but you should show us that you researched existing approaches. As a rule of thumb, it is likely that there are at least 2-3 related works you want to look at. This can be another short section, just tell us how your idea relates to the prior work.

\section{Approach}
This is where you describe what you did. Good things to include are {\color{orange} colorcoding}, pseudocode as in Algorithm~\ref{alg:code} and equations like in Equation~\ref{eq:pi}.
Write enough so that we understand your method without looking at any code.

\begin{algorithm}[H]
    \caption{A great RL algorithm.}
    \label{alg:code}
    \begin{algorithmic}
        \Require environment $e$, algorithm $A$
        \Return policy $\pi$
        \While TRUE
            \State Train $A$ on $e$
        \EndWhile
    \end{algorithmic}
\end{algorithm}

\begin{equation}
    \label{eq:pi}
    \pi \in \Pi, \pi: \mathcal{S} \mapsto \mathcal{A}
\end{equation}

\section{Experiments}
Here are your results and their description. Some things to look out for:
\begin{itemize}
    \item Use a high dpi when plotting
    \item Even better: plot SVGs and use the corresponding LaTeX package to include them
    \item Don't make us zoom in to read your axis descriptions!
\end{itemize}
You should also describe what you see in the plots and how you interpret your results.

\section{Discussion}
Here you recap what you did, say what worked and what didn't, and point toward future work.
Refer back to your research question: did you answer it? How could it be extended in the future?

% Everything from this point on does not count towards your page count
\newpage
\bibliography{references}
\bibliographystyle{plainnat}

\newpage
\section*{Checklist}
This checklist is not mandatory, but can help you set up your project in a reproducible manner.
Options for filling it out are:
\answerYes{}
\answerNo{}
\answerNA{}
\begin{enumerate}

\item General points:
\begin{enumerate}
  \item Do the main claims made in the abstract and introduction accurately reflect your contributions and scope?
    \answerTODO{}
  \item Did you cite all relevant related work?
    \answerTODO{}
  \item Did you describe the limitations of your work?
    \answerTODO{}
  \item Did you include a discussion of future work?
    \answerTODO{}
\end{enumerate}

\item If you are including theoretical results...
\begin{enumerate}
  \item Did you state the full set of assumptions of all theoretical results?
    \answerTODO{}
	\item Did you include complete proofs of all theoretical results?
    \answerTODO{}
\end{enumerate}

\item If you ran experiments (e.g. for benchmarks)...
\begin{enumerate}
  \item Did you include the code, data, and instructions needed to reproduce the main experimental results (either in the supplemental material or as a URL)?
    \answerTODO{}
  \item Did you specify all the training details (e.g., data splits, hyperparameters, how they were chosen)?
    \answerTODO{}
  \item Did you run at least 10 repetitions of your method?
    \answerTODO{}
  \item Did you report error bars (e.g., with respect to the random seed after running experiments multiple times)?
    \answerTODO{}
  \item Did you include the total amount of compute and the type of resources used (e.g., type of GPUs, internal cluster, or cloud provider)?
    \answerTODO{}
\end{enumerate}

\item If you are using existing assets (e.g., code, data, models) or curating/releasing new assets...
\begin{enumerate}
  \item If your work uses existing assets, did you cite the creators?
    \answerTODO{}
  \item Did you make sure the license of the assets permits usage?
    \answerTODO{}
  \item Did you reference the assets directly within your code and repository?
    \answerTODO{}
\end{enumerate}
\end{enumerate}
\end{document}
